Reanalysis Step 9: Alternative Propensity Score Specifications

### 2025-09-07 reanalysis-4-propensity_scores.qmd
refactor outcome model support

# Get list of existing cache files with their modification times
if (use_cache) {
  cache_files <- list.files(cache_dir, pattern = "^twang_imp_.*\\.rds$", full.names = TRUE)
  if (length(cache_files) > 0) {
    cache_info <- file.info(cache_files)
    cache_info$file <- basename(rownames(cache_info))
    cache_info$age_days <- as.numeric(difftime(Sys.time(), cache_info$mtime, units = "days"))
    log_message(paste0("Found ", nrow(cache_info), " cached files in ", cache_dir))
    log_message(paste0("Cache staleness threshold: ", cache_max_age_days, " days"))
  } else {
    cache_info <- NULL
    log_message("No cached files found")
  }
} else {
  log_message("Cache disabled - will recompute all imputations")
}

@@

  # Check for cached result
  cache_file <- file.path(cache_path, paste0("twang_imp_", i, ".rds"))

@@

```{r cache-summary}
# Check cache status
cache_files <- list.files(cache_dir, pattern = "twang_imp_.*\\.rds", full.names = FALSE)
n_cached <- length(cache_files)

>>>>

# Get list of existing cache files with their modification times
if (use_cache) {
  cache_files <- list.files(cache_dir, pattern = "^twang_gbm_imp.*\\.rds$", full.names = TRUE)
  if (length(cache_files) > 0) {
    cache_info <- file.info(cache_files)
    cache_info$file <- basename(rownames(cache_info))
    cache_info$age_days <- as.numeric(difftime(Sys.time(), cache_info$mtime, units = "days"))
    log_message(paste0("Found ", nrow(cache_info), " cached files in ", cache_dir))
    log_message(paste0("Cache staleness threshold: ", cache_max_age_days, " days"))
  } else {
    cache_info <- NULL
    log_message("No cached files found")
  }
} else {
  log_message("Cache disabled - will recompute all imputations")
}

@@

  # Check for cached result (using consistent naming without underscore)
  cache_file <- file.path(cache_path, paste0("twang_gbm_imp", i, ".rds"))

@@

```{r cache-summary}
# Check cache status
cache_files <- list.files(cache_dir, pattern = "twang_gbm_imp.*\\.rds", full.names = FALSE)
n_cached <- length(cache_files)

### 2025-09-07 reanalysis-9-alternative_specifications.qmd
file naming bug
refactor outcome model support

# Cache configuration
use_cache <- TRUE
cache_dir <- file.path(reanalysis_data_dir, "ps_alternative_methods")

@@

results <- run_alternative_ps_analysis(
  imputed_datasets = imputed_datasets,
  ps_formula = ps_formula,
  outcome_formula = outcome_formula,
  mode = analysis_mode,
  cache_dir = cache_dir,
  use_cache = use_cache,
  all_methods = all_methods,
  force_rerun = force_rerun  # Controls whether to reprocess cached results
)

@@

# Check if we have results
if (length(pooled_results) == 0) {
  cat("\n\n*** WARNING: No pooled results available ***\n")
  cat("This could mean:\n")
  cat("1. PS methods haven't been run yet (check reanalysis-4-propensity_scores.qmd)\n")
  cat("2. Cache directory path is incorrect\n")
  cat("3. Cache files have been deleted\n\n")
  cat("Current cache directory:", cache_dir, "\n")
  cat("Looking for files like: nearest_glm_imp_1.rds\n\n")

>>>>

# Cache configuration
use_cache <- TRUE
cache_dir <- file.path(reanalysis_data_dir, "ps_cache")  # Now using unified ps_cache
outcome_cache_dir <- file.path(reanalysis_data_dir, "outcome_cache")  # Separate outcome cache

@@

results <- run_alternative_ps_analysis(
  imputed_datasets = imputed_datasets,
  ps_formula = ps_formula,
  outcome_formula = outcome_formula,
  mode = analysis_mode,
  cache_dir = cache_dir,
  outcome_cache_dir = outcome_cache_dir,
  use_cache = use_cache,
  all_methods = all_methods,
  force_rerun = force_rerun  # Controls whether to reprocess cached results
)

@@

# Check if we have results
if (length(pooled_results) == 0) {
  cat("\n\n*** WARNING: No pooled results available ***\n")
  cat("This could mean:\n")
  cat("1. PS methods haven't been run yet (check reanalysis-4-propensity_scores.qmd)\n")
  cat("2. Cache directory path is incorrect\n")
  cat("3. Cache files have been deleted\n\n")
  cat("Current cache directory:", cache_dir, "\n")
  cat("Looking for files like: nearest_glm_imp1.rds or bart_imp1.rds\n\n")
